Planar Maximal Covering with Ellipses

### 2019-04-27 quali/quali.presentation/slides.tex
WIP

		\item Can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
	\end{itemize}

@@

\section{Cobertura Maximal por Ellipses}

\begin{frame}{Cobertura Maximal por Ellipses}
	content... trabalhos passados
\end{frame}

>>>>

		\item It can be implemented in $K\log{n}$ where $K$ is the number of intersections. 
	\end{itemize}

@@

\section{Maximal Covering by Ellipses}

\begin{frame}{Maximal Covering by Ellipses}
	Let $MCE(\Pp, a, b)$ be an instance of the maximal covering by one ellipse, with $E$ being an ellipse with shape parameters $(a,b) \in \R_{>0}^2$, an optimal solution of $MCE(\Pp, a, b)$ is given by

	\begin{equation*}
	\max_q |\Pp \cap (q)|,
	\end{equation*}

	\begin{itemize}
		\item $E(q)$ is an axis-parallel ellipse with shape parameters $(a,b) \in \R^2_{>0}$.
		\item Assuming unit weights for now
		\item Same algorithm for one disk
	\end{itemize}
